---
title: "678 Final Project Report"
author: "Haochen Pan"
date: "2022-12-05"
output: html_document
---
## Part1 Abstract
In the database recommended by Japanese animation, I found data about a large number of animation ratings, including numerical data such as animation scores, number of participants, and variables of more than 10 groups such as producer and source. This report will use multilevel modeling and other methods to analyze: 1. how popularity and number of community fans and other variables affect the rating of anime; 2. what variables cause high rating animes. The first 10 page will focus on multilevel modeling and other useful visulizations and analysis will in the Appendix part. 

## Part2 Introduction
The name of the data set from Kaggle is called "anime recommendation", which contains information on user preference data from 73,516 users on 12,294 anime. In the excel from the data, some useful variables can be used to find which variables can affect the rating of animes and how they exactly affect the rating. The following contents are the explanation of each variable. 

Anime_id: myanimelist.net's unique id identifying an anime.
Title: full name of anime.
Type: Movie, TV, Special, etc.
Producer: Different producer companies that produce the anime.
Studio: The creator company of anime.
Rating: Average rating out of 10 for this anime.
ScoreBy: Number of people who rate the anime.
Popularity: The popularity of the anime(the lower number means more famous).
Members: Number of community fans that are in this anime's
"group".
Episodes: How many episodes in this show. (1 if movie).
Source: The source of the anime, including Manga, original, etc.
Aired: The date that the anime start to show.

## Part3 Methods

### Data Cleaning
In the uploading part, I delete the missing data and NAs.Then I choose 2 dataframes, the raw data and the data ranked by top-50-rating. 


```{r,echo=FALSE, message=FALSE, warning=FALSE}
library(readr)
anime <- read_csv("https://raw.githubusercontent.com/HaochenPan857/678-final/main/Anime_data1.csv")
data1 <- anime[c("Anime_id","Title", "Type", "Producer", "Studio", "Rating", "ScoredBy", "Popularity","Members","Episodes","Source","Aired","Genre")]
data = na.omit(data1)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(ggthemes)
library(RColorBrewer)
library(grid)
library(gridExtra)
library(ggrepel)
library(tidyr)
library(plotly)
library(corrplot)
library(tidyverse)
library(sf)
library(ggpubr)
library(knitr)
library(coefplot)
library(plotrix)
library(cluster)
library(factoextra)
library(tidytext)
library(tm)
library(stm)
library(reshape2)
library(wordcloud)
library(RColorBrewer)
library(MASS)
library(lme4)
library(lattice)
data2 <- data %>%
  mutate(Source = str_replace(Source,"[[0-9]]+(?!-)","Undicided"))
library("data.table") 
data_top50 <- data[order(data2$Rating, decreasing = TRUE), ]
data_top50 <- head(data_top50, 50)
```

### EDA
Before the linear regression and modeling, I first use some variables mentioned above to make graphs to predict which methods are more useful in the next parts. 1 of the graphs is used more are in part 6. 

```{r,echo=FALSE, message=FALSE, warning=FALSE}
sample_1 = sample_n(data, 200)
ggplot(data = sample_1, mapping = aes(x = Rating, y = Popularity)) +
  geom_point(alpha = 0.5, aes(size = Members , color=Source)) +
   scale_x_discrete(breaks = seq(0, 100, by = 5)) +
  ggtitle("figure2:Relationship between rating and Members/Source") +
  xlab("The rating of animes") + ylab("Popularity") 
```

In figure 1 to 3, I randomly select 100 of the animes from the data to see the changes of ratings and how other variables can affect them. In a short conclusion, some sources like manga, some types like TV, more popularity and more members seems to have a higher rating in the graph. While the scoring people will not have strong relationship, As a result, I plan to focus on this variables. 

### Linear Model
First, I use linear model to analysis how Popularity/Members affect Rating. The graphs/summary/conclusion are in part 6. 

### Multilevel Modeling
Then, based on the requirement, i use the multilevel model to analysis and predict the data.Due to the page limit, I will choose Source/Type for different model and visualization. Analysis about what are missing are in part 6.

#### First, I check the distributions by source. 
```{r, echo=FALSE, message=FALSE, warning=FALSE}
data2 %>% 
  group_by(Source) %>% 
  summarise(mean = mean(Rating, na.rm = T), 
            SD = mean(Rating, na.rm = T), 
            miss = mean(is.na(Rating))) %>% 
  mutate_if(is.numeric, ~round(., 2)) %>% 
  print(n = 50)
data2 %>%
  ggplot(aes(Rating)) + 
  geom_density() +
  facet_wrap(~Source)
```

#### Then I tried lmer model with Source
```{r,echo=FALSE, message=FALSE, warning=FALSE}
mu5 <- lmer(Rating ~ 1 + (1 |Source),REML= FALSE,
          data = data2)
summary(mu5)
data2$mu5 <- predict(mu5)
data2 %>% 
  ggplot(aes(Members, mu5, color = Source, group = Source)) + 
  geom_smooth(se = F, method = lm) +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks = element_blank()) +
  ggtitle("figure5:Prediction for Rating based on Source and Members")+
  labs(x = "", y = "change for Rating", color = "Source")
qqmath(ranef(mu5, condVar = TRUE))
```

Figure 5 allows each source to have a different average change in rating through the random effect. I also visualize these random effects in a qqmath.
In this graph each dot represents a source and the line around it is the confidence interval. The 0 on the x axis is the intercept or expected value. So the most source have values significantly different from that, again indicating that this is a relevant level for the analysis.

#### Then I try the prediction in MLM models for Type and Member
```{r,echo=FALSE, message=FALSE, warning=FALSE}
mu3 <- lmer(Rating ~ 1 + Members + (1 |Type),REML= FALSE,
          data = data2)
summary(mu3)
data2$mu3 <- predict(mu3)
data2 %>%
  ggplot(aes(Members, mu3, color = Type, group = Type)) + 
  geom_smooth(se = F, method = lm) +
  theme_bw() +
  ggtitle("figure6:Prediction in MLM model")+
  labs(x = "Members", y = "change for Rating", color = "Type")
``` 

Here the result shows as member of fans increases by 1 the expected increase for rating is 3.072e-06. The intercept now is understood as the expected increase of rating when the independent variable is 0. I visualize the relationship between the two variables as implied by our model in figure 6. 

#### In the next step we try random slope model for Type/Member.
```{r,echo=FALSE, message=FALSE, warning=FALSE}
mu4 <- lmer(Rating ~ 1 + Members + (1 + Members |Type),REML= FALSE,
          data = data2)
summary(mu4)
data2$mu4 <- predict(mu4)
data2 %>%
  ggplot(aes(Members, mu4)) + 
  geom_smooth(se = F, method = lm, size= 1) +
  stat_smooth(aes(color = Type, group = Type),
              geom = "line", alpha = 0.4, size = 1)+
  theme_bw()+
  guides(color = F)+
   ggtitle("figure8:Prediction in random slope model")+
  labs(x = "Members", y = "change in rating", color = "Type")
qqmath(ranef(mu4, condVar = TRUE))
```

In the model, the Member variable is slightly smaller and that we have a new coefficient in the random part of the model. The variance of the random slope for member is 1.67e-08.This coefficient is hard to interpret on its own. So I draw another graph which is fig8. Some types' members is more important than others. The dot plot also makes sense. 

```{r,echo=FALSE, message=FALSE, warning=FALSE}
coefs_mu4 <- coef(mu4)
coefs_mu4$Type %>%
  mutate(Type = rownames(coefs_mu4$Type))  %>% 
  ggplot(aes(Members, `(Intercept)`, label = Type)) + 
  geom_point() + 
  geom_smooth(se = F, method = lm) +
  geom_label(nudge_y = 0.15, alpha = 0.5) +
  theme_bw() +
  ggtitle("figure10 :effect of members and rating")+
  labs(x = "Slope", y = "Intercept")
```

In figure10 The graphs shows that we can divide the types into 3 parts. TV and Movie have most members and high increasing in rating but low effect of members to outcome. The Music has low support in rating but members for music has strong effect.

### K-means algorithm
For this part, I want to use k-means to cluster observations and want observations in the same group to be similar and observations in different groups to be dissimilar. The visulization is in part 6.

### Word Could and Tpoic Modeling

Finally, I tried what I learn in 615 to analysis the non-numerical data.The word cloud shows the hot topics for data_top50. More details are in part 6.
```{r,echo=FALSE, message=FALSE, warning=FALSE}
word_data <- data_top50[c("Genre")]
word_data <- na.omit(word_data)
word_data_df <- tibble(word_data)
word_data_df %>% 
  mutate(Genre_number = row_number()) -> word_data_df
word_data_df <- word_data_df %>%
  unnest_tokens(word, Genre, to_lower = FALSE)%>% anti_join(stop_words)
word_data_df %>% 
count(word, sort = TRUE)
word_data_df %>%
  count(word, sort = TRUE) %>%
  filter( n>10) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word)) +
  geom_col() +
  labs(y = NULL,
       title = "Word Frequency from Genre") +
  xlab("Count of word")+
  ylab("Most frequent word")
world_cloud <- wordcloud(words = word_data$Genre,max.words = 150, min.freq = 1, random.order = FALSE,rot.per = 0.35, colors=brewer.pal(8, "Dark2"))
```

If we compare the topics, we can see what kind of topics in genre are more likely to be shown in the top rating animes. 

## Part4 Results
Based on the modeling above, there results are:
1. More Popularity and More members of fan groups are more likely to increase the rating for animes, while the scoring people do not have strong relationship. The different type and source also make sense. 
2. Multilevel modeling distribution works well on type/source, for the members value as the x-label, some specific type/source are more effective in rating, like OVA, Special/ Manga and game.The random effects are changing for different model. This indicates that number of members for group is explaining some variation.
3. There are some words that show high frequency in the genre part, which means high rating animes are often related to some of the words. 

## Part5 Discussion
Based on the results, especially for the prediction part, the members and popularity are the most 2 important numerical variables that affect the rating. More popularized and discussed anime are easier to get rating higher than average. However, the groups of type and source may be different in different situations. For example, TV type of animes have more members to discuss, but the effect to increase the rating is not that important. In the future, the type of animes will still be TV-mained, but if more people start to become members of other types, there rating will increase faster than TV. Also, it will be harder to get higher rating when evaluating the date of anime(no space to show in the pdf) and about the genre, animes about comedy, action and advanture will still be the main topics for anime. 

## Part6 Appendix and more things

1. EDA:The geom_bar for variable "Source" and this count
```{r,echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data = data2)+
  geom_bar(mapping = aes(x = Source, fill= Source)) +
   scale_x_discrete(breaks = seq(0, 100, by = 5)) +
  ggtitle("figure1:Number of different sources") +
  xlab("Sources") + ylab("Number of sources")
```

2. EDA:The geom_point for variable "Type" and "ScoredBy" with Rating
```{r,echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data = sample_1, aes(x = Rating, y = ScoredBy)) +
  geom_point(data = sample_1, size = 1.0, alpha = 1.0, aes(color= Type)) +
  scale_x_discrete(breaks = seq(0, 100, by = 5))  +
  ggtitle("figure3:Relationship between rating and ScoredBy/type") +
  xlab("Rating of the animes") + ylab("ScoredBy")
```

3. Linear Model
```{r, echo=FALSE, message=FALSE, warning=FALSE}
M1 = lm(Rating ~ log(Popularity)+ log(Members)+ log(ScoredBy), data = data2)
summary(M1)
kable(confint(M1), digits = 2)
plot(M1)
coefplot(M1)
```

In simple linear model, the model complies with the assumptions of normality and constant variance, so there is no issue about violating the model assumptions. More popularity score(less popular) will decress the rating with 0.10502 , more community fans and scored people will increase the rating with 0.19808 and 0.01965. 

4. Multilevel Modeling distribution about Type/ Studio/Producer
```{r, echo=FALSE, message=FALSE, warning=FALSE}
data2 %>% 
  group_by(Type) %>% 
  summarise(mean = mean(Rating, na.rm = T), 
            SD = mean(Rating, na.rm = T), 
            miss = mean(is.na(Rating))) %>% 
  mutate_if(is.numeric, ~round(., 2)) %>% 
  print(n = 50)
data2 %>%
  ggplot(aes(Rating)) + 
  geom_density() +
  facet_wrap(~Type)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
data_top50 %>%
  ggplot(aes(Rating)) + 
  geom_density() +
  facet_wrap(~Studio)
```

5.  Multilevel Modeling about Type

```{r,echo=FALSE, message=FALSE, warning=FALSE}
mu2 <- lmer(Rating ~ 1 + (1 |Type),REML= FALSE,
          data = data2)
summary(mu2)
data2$mu2 <- predict(mu2)
data2 %>% 
  ggplot(aes(Members, mu2, color = Type, group = Type)) + 
  geom_smooth(se = F, method = lm) +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks = element_blank()) +
  ggtitle("figure4:Prediction for Rating based on Type and Members")+
  labs(x = "", y = "change for Rating", color = "Type")
qqmath(ranef(mu2, condVar = TRUE))
```

6. the prediction in MLM models for Source and Member

```{r,echo=FALSE, message=FALSE, warning=FALSE}
mu6 <- lmer(Rating ~ 1 + Members + (1 |Source),REML= FALSE,
          data = data2)
summary(mu6)
data2$mu6 <- predict(mu6)
data2 %>%
  ggplot(aes(Members, mu6, color = Source, group = Source)) + 
  geom_smooth(se = F, method = lm) +
  theme_bw() +
  ggtitle("figure7:Prediction in MLM model2")+
  labs(x = "Members", y = "change for Rating", color = "Source")
```

7. Random slope model for Source/Member.
```{r,echo=FALSE, message=FALSE, warning=FALSE}
mu7 <- lmer(Rating ~ 1 + Members + (1 + Members |Source),REML= FALSE,
          data = data2)
summary(mu7)
coefs_mu7 <- coef(mu7)
coefs_mu7$Source %>%
  mutate(Source = rownames(coefs_mu7$Source))  %>% 
  ggplot(aes(Members, `(Intercept)`, label = Source)) + 
  geom_point() + 
  geom_smooth(se = F, method = lm) +
  geom_label(nudge_y = 0.15, alpha = 0.5) +
  theme_bw() +
  ggtitle("figure10 :effect of members and rating")+
  labs(x = "Slope", y = "Intercept")
```

In the Source part, the random slope model is not useful in plotting the prediction. But the Coef plot is useful to analysis. 

8. k-mean
```{r,echo=FALSE, message=FALSE, warning=FALSE}
data3 <- data2[c("Anime_id","Rating","Members","Popularity")]
data3 <- sample_n(data3,40)
data3 <- na.omit(data3)
data3 <- data3[!is.na(as.numeric(data3$Rating)),]
data3 <- data3[!is.na(as.numeric(data3$Popularity)),]
data3 <- data3[!is.na(as.numeric(data3$Members)),]
data3 <- data3[!is.na(as.numeric(data3$Anime_id)),]
data3 <- scale(data3)
distance <- get_dist(data3)
fviz_dist(distance, gradient = list(low = "#00AFBB", mid = "white", high = "#FC4E07"))
k <- kmeans(data3, centers = 2, nstart = 40)
str(k)
k
fviz_cluster(k, data = data3)
```

9. Topic modeling
Finally, I tried what I learn in 615 to analysis the non-numerical data.
```{r,echo=FALSE, message=FALSE, warning=FALSE}
word_data <- anime[c("Genre")]
word_data <- na.omit(word_data)
word_data_df <- tibble(word_data)
word_data_df %>% 
  mutate(Genre_number = row_number()) -> word_data_df
word_data_df <- word_data_df %>%
  unnest_tokens(word, Genre, to_lower = FALSE)%>% anti_join(stop_words)
word_data_df %>% 
count(word, sort = TRUE)
#plot frequencies
word_data_df %>%
  count(word, sort = TRUE) %>%
  filter( n>1000) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word)) +
  geom_col() +
  labs(y = NULL,
       title = "Word Frequency from Genre") +
  xlab("Count of word")+
  ylab("Most frequent word")
world_cloud <- wordcloud(words = word_data$Genre,max.words = 150, min.freq = 1, random.order = FALSE,rot.per = 0.35, colors=brewer.pal(8, "Dark2"))
```